Figures to insert in text

### 2018-03-12 Chapters/Chapter02.tex
SDM Minor change in generalized reading.
sdm ch2

It is interesting that Kanerva has proposed $z=1$ without realizing the generalized reading. Even so, he proposed the optimal $z$ --- the one with the highest critical distance.

@@

My advisor, Alexandre Linhares, has proposed another read operation: an information-theoretical weighted reading. In it, the sum of the counter's value is weighted based on the distance between each hard-location's address and the reading address. The logic behind it is to vary the importance of each hard-location inside the circle.  It is only natural that one encodes an item in closer hard locations with a stronger signal, and a natural candidate for this signal function is the amount of information contained in the distance between the item and each hard location.  Closer hard locations have lower probabilies and therefore should encode more information.

>>>>

It is interesting that Kanerva has proposed $z=1$ without realizing the generalized reading. Even so, he proposed the $z$ with the highest critical distance.

@@

My advisor, Alexandre Linhares, has proposed another write operation: an information-theoretical weighted write. In it, the sum of the counter's value is weighted based on the distance between each hard-location's address and the reading address. The logic behind it is to vary the importance of each hard-location inside the circle.  It is only natural that one encodes an item in closer hard locations with a stronger signal, and a natural candidate for this signal function is the amount of information contained in the distance between the item and each hard location.  Closer hard locations have lower probabilies and therefore should encode more information.

### 2018-03-12 Chapters/sdm-applications.tex

This is a simplified analysis because it does not take into consideration the hardlocations shared by the different letters. It works fine for our example because letter ``I'' and ``T'' share, on average, zero hardlocations.

@@

In the learning phase, noisy images are generated and they are written into SDM chunked with their labels. The chunk was calculated using the exclusive or (XOR) operator. So, the image bitstring was written to the address of its bitstrings XOR its label bitstring --- write(addr=bs\_image $\oplus$ bs\_label, datum=bs\_image).

Finally, in order to remove the noise of a new image, first we have to classify it (possibly using the already presented classification algorithm), and then we just have to read from the chunked address until it converges.

>>>>

This is a simplified analysis because it does not take into consideration the hardlocations shared by the different letters. It works fine for our example because letter ``I'' and ``T'' are almost orthogonal and share, on average, only one hardlocation.

@@

If the intersection between images becomes too high, the noise filter stops working. We have confirmed it writing letters ``B'', ``C'', ``D'' and numeral ``8''. They share a great amount of hard-locations and our noise filter stopped working. The training sets can be seen in Figure \ref{fig:filter-training2} and the results in Figure \ref{fig:filter-results2}.

A possible solution to this interference problem is to use labels. Each label has a random bitstring, which will be chuncked with the images before writing into SDM. Hence, before reading, we also have to chunck the image with the label --- which means we need to know the label of each image. The chunk was done using the exclusive OR (XOR) operator, i.e., $bs\_chunck = bs\_image \oplus bs\_label$. In other words, we run \lstinline{write(address=bs_chunk, datum=bs_label)} during the training, and \lstinline{read(address=bs_chunk)} during the testing. We used the same training set as before, and the results can be seen in Figure \ref{fig:filter-results2-chunk}.

The chunck through exclusive OR (XOR) works because of the following theorem:

\begin{theorem}
If $v_1$ and $v_2$ are random bitstrings, then $\forall a, b, \mathbf{E} \left[ d(a \oplus v_1, b \oplus v_2) \right] = n/2$.
\end{theorem}
\begin{proof}
Let $\mathbb{A} = \{ i | a^i = b^i \}$ be the indexes in which the bits of $a$ are equal to the bits of $b$, and $\mathbb{B} = \{ i | a^i \ne b^i \}$ be indexes in which the bits of $a$ are different from the bits of $b$. Thus,

\begin{align*}
d(a \oplus v_1, b \oplus v_2) &= \sum_{i=1}^n d(a^i \oplus v_1^i, b^i \oplus v_2^i) \\
    &= \sum_{i=1}^n (a^i \oplus v_1^i) \oplus (b^i \oplus v_2^i) \\
    &= \sum_{i=1}^n (a^i \oplus b^i) \oplus (v_1^i \oplus v_2^i) \\
    &= \sum_{i \in \mathbb{A}} (a^i \oplus b^i) \oplus (v_1^i \oplus v_2^i) +
       \sum_{i \in \mathbb{B}} (a^i \oplus b^i) \oplus (v_1^i \oplus v_2^i)
\end{align*}

For $i \in \mathbb{A}$, $a^i \oplus b^i = 0$, and follows:

\begin{align*}
(a^i \oplus b^i) \oplus (v_1^i \oplus v_2^i) &= 0 \oplus (v_1^i \oplus v_2^i) \\
    &= v_1^i \oplus v_2^i \\
    &= d(v_1^i, v_2^i)
\end{align*}

Hence, $\mathbf{E} \left[ \sum_{i \in \mathbb{A}} d(a^i \oplus v_1^i, b^i \oplus v_2^i) \right] = \mathbf{E} \left[ \sum_{i \in \mathbb{A}} d(v_1^i, v_2^i) \right] = |\mathbb{A}|/2$, because $v_1$ and $v_2$ are random bitstrings and their average distance is half the number of bits.

For $i \in \mathbb{B}$, $a^i \oplus b^i = 1$, and follows:

\begin{align*}
(a^i \oplus b^i) \oplus (v_1^i \oplus v_2^i) &= 1 \oplus (v_1^i \oplus v_2^i) \\
    &= d(1, v_1^i \oplus v_2^i)
\end{align*}

Hence, $\mathbf{E} \left[ \sum_{i \in \mathbb{B}} d(a^i \oplus v_1^i, b^i \oplus v_2^i) \right] = \mathbf{E} \left[ \sum_{i \in \mathbb{B}} d(1, v_1^i \oplus v_2^i) \right] = |\mathbb{B}|/2$.

Finally, $\mathbf{E} \left[ d(a \oplus v_1, b \oplus v_2) \right] = |\mathbb{A}|/2 + |\mathbb{B}|/2 = n/2$, since $|\mathbb{A}| + |\mathbb{B}| = n$
\end{proof}

In our example, we just used the right label to read each image. But, we could have used our classification algorithm already presented in this work as a pre-processing step, and then, with the correct label, run the noise filter.
